\documentclass[]{article}

\usepackage{amsmath, amssymb} % Math formatting and symbols
\usepackage{graphicx} % Insert graphics
\usepackage{wrapfig} % Allow text to wrap around images
\usepackage[cm]{fullpage} % Smaller margins and header/footer
\usepackage{setspace}
\usepackage{gensymb} % degree symbol

\usepackage{float}

\usepackage{enumitem} % Allow for widest tag in enumerate

\renewcommand*\descriptionlabel[1]{\hspace\leftmargin$#1$}

\newenvironment{adescription}[1]
{\begin{list}{}%
		{\renewcommand\makelabel[1]{##1\hfill}%
			\settowidth\labelwidth{\makelabel{#1}}%
			\setlength\leftmargin{\labelwidth}
			\addtolength\leftmargin{\labelsep}}}
	{\end{list}}

\newcommand{\bd}{\textbf}
\newcommand{\dquad}{\quad{}\quad{}}

\title{\vspace{-5ex}Examples \vspace{-5ex}}
\author{}
\date{}

\begin{document}
	\setstretch{0.82}
	\maketitle{}
	
	\subsection*{Symbols}
	\begin{align*}
		n \text{ choose } x = {n \choose x}
	\end{align*}
	
	\subsection*{Children}
	\par In a \bd{four-child} family, what are the odds of the following?
	\begin{equation*}
		\text{Total} = 2^4 = 16
	\end{equation*}
	(a) Three girls and a boy in the family?
	\begin{equation*}
		\frac{4!}{3!1!} = \frac{24}{6} = 4
	\end{equation*}
	(b) A youngest child in the family who is a girl?
	\begin{equation*}
		1 * 2^3 = 8
	\end{equation*}
	(c) An oldest child and a youngest child in the family who are both boys
	\begin{equation*}
		1 * 2^2 * 1 = 4
	\end{equation*}

	\subsection*{Cards}
	\begin{equation*}
		\text{Total} = {52 \choose \text{Number drawn}}
	\end{equation*}
	\noindent When drawing \bd{one card} what are the odds it is a \bd{club} or \bd{jack}?
	\begin{equation*}
		13 + 4 - 1 = 16
	\end{equation*}

	\noindent When drawing \bd{two cards} What are the odds it is a \bd{pair}?
	\begin{equation*}
		13 * {4 \choose 2}
	\end{equation*}
	
	\subsection*{Coin}
	\par A coin is tossed \bd{six} times. What are the odds of the following?
	\begin{equation*}
		\text{Total} = 2^6 = 64
	\end{equation*}
	(a) What are the odds the coin lands on heads more than one?
	\begin{equation*}
		1 - \frac{{6 \choose 0} + {6 \choose 1}}{\text{Total}} = 1 - \frac{7}{64}
	\end{equation*}
	(b) The coin lands on heads exactly 2 times?
	\begin{equation*}
		{6 \choose 2}
	\end{equation*}

	\subsection*{Defection}
	\par Lots of 36. Sample of 8. Any defective = rejection. Contains 2 defective. What are the odds of shipping?
	\begin{equation*}
		\text{Total} = {36 \choose 8}
	\end{equation*}
	\begin{align*}
		34 \choose 8
	\end{align*}

\end{document}