\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{WikiLeaks’ Julian Assange fights extradition to the U.S. in top London court}
		}
	\end{center}
	\par Julian Assange created WikiLeaks, a wistleblowing site used to host classified government documents, in the early 2000s. After taking refuge in a an Ecuadorean embassy located in London for many years, he was forced to leave when Ecuador revoked his citizenship. Assange has a warrant out for his arrest in the United States, as well as other countries and faces being extradited and consequently arrested and jailed for life.
	
	\begin{itemize}[label=--]
		\item What nations embassy was Julian Assange staying in, before losing citizenship? \textbf{Ecuador}
		\item What organization did Julian Assange start? \textbf{WikiLeaks}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.cnbc.com/2020/09/08/wikileaks-julian-assange-fights-extradition-to-the-us-in-london-court.html
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{The Air Force just tested 'robot dogs' to help security forces keep an eye on their bases}
		}
	\end{center}
	\par A Nevada Air Force base just started testing out a very unique surveillance system--robot dogs. They can provide communication through both video and audio as well as being able to hopefully navigate complex terrain. If these prototypes work they would definitely change up the scene on Air Force bases.
	
	\begin{itemize}[label=--]
		\item What new security technique did the Air Force test out? \textbf{Robot Dogs}
		\item Which state was the Air Force base was used to test the robot dogs located in? \textbf{Nevada}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.businessinsider.com/air-force-tests-robot-dogs-to-support-base-security-forces-2020-9
\end{document}