\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{49ers close facility after Bourne’s positive COVID-19 test}
		}
	\end{center}
	\par Receiver Kendrick Bourne of the 49ers recently tested positive for COVID-19, but it doesn't seem to be shaking many plans. Though the 49ers facility is shutting down, the 49ers themselves still plan to play against Green Bay Thursday. He was instantly placed on the COVID-19 list and began self-quarantining.
	
	\begin{itemize}[label=--]
		\item What NFL team had their wide receiver, Kendrick Bourne, test positive for COVID-19 recently? \textbf{The 49ers}
		\item Even after a player testing positive for COVID-19, the 49ers still plan to play what team this Thursday? \textbf{Green Bay Packers}
	\end{itemize}

	\noindent
	\emph{Source:} https://apnews.com/article/nfl-sports-virus-outbreak-football-san-francisco-6b0cd0e28af22e6e804d0e9206470bcf
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Portland, Maine, bans police from using facial recognition software}
		}
	\end{center}
	\par Citizens from Portland, Maine had many big decisions to vote on during Super Tuesday, one of which was the use of facial recognition by law enforcement. They passed the ballot initiative, which banned it as well as giving citizens the ability to sue the city for illegal surveillance if they violate it. This was following a trend of other cities, such as San Francisco; Oakland; Boston and Cambridge; and Massachusetts, and is likely to be followed by more.
	
	\begin{itemize}[label=--]
		\item What city recently passed a ballot initiative to ban the use of facial recognition by law enforcement? \textbf{Portland, Maine}
		\item What did Portland, Maine ban-following a list of other cities? \textbf{The use of facial recognition by law enforcement}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.cnet.com/news/portland-maine-bans-police-from-using-facial-recognition-software/
\end{document}
