\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{U.S. expected to sue Google next week as DOJ seeks support from states}
		}
	\end{center}
	\par The U.S. Justice Department plans to sue Google over its alleged anti-competitive practices. One of the primary practices that are likely to be addressed is Google's deprival of user data and preferences from rivals, such as Bing. Unsurprisingly, since the time of this information being released Google has denied any wrongdoing.
	
	\begin{itemize}[label=--]
		\item What company is likely to have an anti-trust lawsuit brought against them next week? \textbf{Google}
		\item Who is planning to sue Google? \textbf{The US/DOJ (\emph{Department of Justice)}}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.reuters.com/article/tech-antitrust-google/us-expected-to-sue-google-next-week-as-doj-seeks-support-from-states-idUSL1N2GQ24S
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Hawaii defense contractor charged with \$12.8m coronavirus relief fraud}
		}
	\end{center}
	\par Though many businesses and people are struggling in the face of the corona virus pandemic, some are working to take advantage of it. Martin Kao, a Hawaii-based defense contractor, is one of these people; he worked to falsify loan applications and abuse the system in place to assist small businesses. He has recently been arrested and faces the charges of bank fraud and money laundering.
	
	\begin{itemize}[label=--]
		\item A defense contractor based in which state is charged with stealing \$12.8 million in Covid-19 funds? \textbf{Hawaii}
		\item What did Martin Kao do recently that got him in the news? \textbf{Stole millions in Covid-19 relief funds}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.msn.com/en-us/news/politics/hawaii-defense-contractor-charged-with-12-8m-coronavirus-relief-fraud/ar-BB19ARtm
\end{document}