\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{Charlie Brown specials to air on TV, after all, in PBS deal}
		}
	\end{center}
	\par Recently, Apple, who had bought the rights to Charlie Brown, announced that it would not be airing on TV this year. This caused a wave of public backlash, which prompted a change. In response, Apple recently announced that the Thanksgiving and Christmas specials would be aired this year. This is upon their original plan to have it free on their Apple TV+ platform for a three-day window.
	
	\begin{itemize}[label=--]
		\item Who just got back on TV? \textbf{Charlie Brown}
		\item Charlie Brown got put back on TV for which two holidays? \textbf{Thanksgiving and Christmas}
	\end{itemize}

	\noindent
	\emph{Source:} https://apnews.com/article/television-broadcast-television-f644d4ee03e7eaa9f9fdff8cee5a82ba
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Bitcoin Hits \$18K As Investors Anticipate ‘Shallow’ Pullback Before New Highs}
		}
	\end{center}
	\par Recently, Bitcoin hit \$18k, a number that had not been reached since three years prior during the Bitcoin bubble. Analysts have predicted that there will be a slight decrease but another spike following that. It's estimated that during this spike prices could reach as high as 19k. The all time high was \$19,763 in December of 2017, so predictions don't place it far off of creating a new record. However, it's impossible to say how the market will react and whether reaching the all time high will cause another drop.
	
	\begin{itemize}[label=--]
		\item What high did Bitcoin reach recently? \textbf{\$18k}
		\item Do analysts predict Bitcoin will fall drastically or continue to rise? \textbf{Continue to rise}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.cryptovibes.com/blog/2020/11/18/bitcoin-hits-18k-as-investors-anticipate-shallow-pullback-before-new-highs/
\end{document}
