\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{Software company founder McAfee charged with tax evasion}
		}
	\end{center}
	\par Entrepreneur and founder of McAfee Antivirus, John McAfee has lived a very complex and complicated life, with the most recent event being a charge for tax evasion. He currently is being held in Spain, while his extradition into the U.S. is pending. After reaching the U.S., he will be charged for tax evasion from failure to report income from promotion of crypto-currency while doing consulting work, and he faces up to 30 years in prison if convicted.
	
	\begin{itemize}[label=--]
		\item What is John McAfee, founder of McAfee Antivirus, being charged with? \textbf{Tax Evasion}
		\item Who founded an antivirus company and recently got charged with tax evasion? \textbf{John McAfee}
	\end{itemize}

	\noindent
	\emph{Source:} https://apnews.com/article/john-mcafee-indictments-tax-evasion-tennessee-memphis-\\b84dcf47d7fe35e8bd7f9e116999fb38
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Facebook will ban US political ads indefinitely after election}
		}
	\end{center}
	\par Facebook had previously said that they plan to stop showing political ads a week before the election; however, now Facebook has worked to increase that. They plan to wait to re-start showing political ads until after all the votes have been counted and one side has won. They hope this will help to stop candidates from declaring victory falsely or prematurely.
	
	\begin{itemize}[label=--]
		\item What social media site has banned political ads for a week before the election and won't show them until all votes are counted? \textbf{Facebook}
		\item Why has facebook announced a ban of political ads for an undetermined amount of time after Nov 3? \textbf{To stop premature declarations of victory}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.theverge.com/2020/10/7/21506798/facebook-ban-political-ads-after-us-presidential-election-trump-biden-results-notification
\end{document}
