\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{Got any signal up here? Nokia to build mobile network on the moon}
		}
	\end{center}
	\par After recently winning a bid with NASA, Nokia has some big plans. They are planning to build a 4G communication system on the moon. They looked into 5G, however the consistency and reliability from 4G outweighed the potential speed benefits. This network is expected to have construction begin in late 2022, followed by NASA sending humans back to the moon in 2024.
	
	\begin{itemize}[label=--]
		\item What is Nokia planning to do that is pretty \emph{out of this world}? \textbf{Building a 4G network on the moon}
		\item When does NASA plan to send humans back to the moon? \textbf{2024}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.reuters.com/article/nokia-nasa-moon-idUSKBN2741JR
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Justice Dept. files landmark antitrust case against Google}
		}
	\end{center}
	\par This Tuesday, the Justice Department brought a long awaited antitrust lawsuit against google. This is one of the most significant cases intended protect competition since their suit of Microsoft. The suit pertains to abuse by Google of its dominance in online searching and advertising. Its expected that the result of this case will have a ripple effect on other large tech companies that  border on monopolies.
	
	\begin{itemize}[label=--]
		\item Who just sued Google? \textbf{The Department of Justice}
		\item What huge tech companies just got sued for anti-trust violations? \textbf{Google}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.msn.com/en-gb/money/companies/justice-dept-files-landmark-antitrust-case-against-google/ar-BB1ad2RI
\end{document}