\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{China spacecraft lands on moon to bring rocks back to Earth}
		}
	\end{center}
	\par For the first time since 1970, spaceships have been sent out with the intention to bring lunar rocks back to Earth. China's spacecraft landed Tuesday at its intended landing spot. They plan to collect approximately 4 and a half pounds of rock over the course of 2 days by drilling into the surface of the moon. This is significantly less rock than have been obtained in the past (NASA brought back 842 pounds over the course of 3 years).
	
	\begin{itemize}[label=--]
		\item What nation recently sent a probe to the moon? \textbf{China}
		\item Why did China send a probe to the moon? \textbf{To collect rocks and bring them home}
	\end{itemize}

	\noindent
	\emph{Source:} https://apnews.com/article/international-news-china-moon-92f757e0974a0738c71ef2260c7d5795
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Uber completes its \$2.65B deal to buy Postmates}
		}
	\end{center}
	\par Uber has long been interested in the delivery of groceries and other goods, which led to the creation of Uber Eats. However, Uber wanted to capture a larger part of the market, which led to its recent acquisition of postmates. This came at a very lucrative time for Uber, since the pandemic Uber Eats orders increased by over 100\% and its likely postmates saw similar numbers. Though, this was not a cheap endeavor costing well over 2 billion dollars.
	
	\begin{itemize}[label=--]
		\item What service did Uber recently acquire? \textbf{Postmates}
		\item How much did Uber pay for Postmate (to the nearest billion)? \textbf{3 billion}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.cnet.com/news/uber-completes-its-2-65b-deal-to-buy-postmates/
\end{document}
