\documentclass{article}

\usepackage{fullpage}
\usepackage{enumitem}

\title{Current Events}
\author{Gaston Gonnerman}
\date{6th period}

\begin{document}
	\maketitle
	
	\begin{center}
		\large{
			\textbf{Facebook and Google indefinitely extend their ban on political ads}
		}
	\end{center}
	\par In the wake of the recent presidential election, some tech companies have continued their ban of political ads. Many of these companies had planned to get rid of this ban a week after the election occurred. However, the dispute and questioning of the election, primarily by President Trump and the "Stop the steal" movement, has caused this ban to be continued to reduce questions about the winner. They have not yet stated when the bans will be lifted, but they can be expected to continue until at least the runoff senate races are finished.
	
	\begin{itemize}[label=--]
		\item Many large tech companies have continued their ban on what? \textbf{Political Ads}
		\item What movement has been questioning the recent election results? \textbf{The "stop the steal" movement}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.engadget.com/facebook-google-election-ad-bans-170654929.html
	\\ \\ \\
	
	\begin{center}
		\large{
			\textbf{Amazon's Ring video doorbells catch fire because wrong screw used}
		}
	\end{center}
	\par The Amazon Ring is a smart doorbell with video features which has grown to be very popular over the recent years. However, recently there was a recall notice for ~350,000 however users aren't being asked to send them back, only follow new guidelines. The problem was that users had been losing the original safety screw" and replacing it with random screws they have. This has been shown to cause overheating and even catching fire in some cases.
	
	\begin{itemize}[label=--]
		\item What Amazon owned product recently got new guidelines? \textbf{The Amazon Ring}
		\item The Amazon Ring recently had what problem? \textbf{Lighting on fire}
	\end{itemize}

	\noindent
	\emph{Source:} https://www.bbc.com/news/technology-54903754
\end{document}
